---
title: "Project on Statistical Inference Course"
output: html_document
---

##Answers

Question one <- The sample mean is 4.993 while the theoretical mean is 5. The center of distribution in averages of 40 exponentials is very close to the theoretical center of the distribution.
Question two <- Standard Deviation of the distribution is 0.7931608 with the theoretical SD calculated as 0.7905694. The Theoretical variance is calculated as ((1 / ??) * (1/???n))<sup>2</sup> = 0.625. The actual variance of the distribution is 0.6291041
Question three <-Due to Due to the central limit theorem (CLT), the distribution of averages of 40 exponentials is very close to a normal distribution.

```{r DataLoading}
library("data.table")
library("ggplot2")
```


```{r}
set.seed(31)
# our samples
n <- 40
#setting lambda
lambda <- 0.2
# simulations
simulations <- 1000
# simulation
simulated_exponentials <- replicate(simulations, rexp(n, lambda))
# calculate mean of exponentials
means_exponentials <- apply(simulated_exponentials, 2, mean)
```


```{r}
analytical_mean <- mean(means_exponentials)
analytical_mean
```

```{r}
# analytical mean
theory_mean <- 1/lambda
theory_mean
```

```{r}
# visualization
hist(means_exponentials, xlab = "the mean", main = "Simulations of functions")
abline(v = analytical_mean, col = "blue")
abline(v = theory_mean, col = "red")
```

## Question 2

```{r}
# standard deviation of distribution
standard_deviation_dist <- sd(means_exponentials)
standard_deviation_dist
```

```{r}
# standard deviation from analytical expression
standard_deviation_theory <- (1/lambda)/sqrt(n)
standard_deviation_theory
```

```{r}
# variance of distribution
variance_dist <- standard_deviation_dist^2
variance_dist
```

```{r}
# variance from analytical expression
variance_theory <- ((1/lambda)*(1/sqrt(n)))^2
variance_theory
```

## Question 3

```{r}
xfit <- seq(min(means_exponentials), max(means_exponentials), length=100)
yfit <- dnorm(xfit, mean=1/lambda, sd=(1/lambda/sqrt(n)))
hist(means_exponentials,breaks=n,prob=T,col="orange",xlab = "means",main="Density of means",ylab="density")
lines(xfit, yfit, pch=22, col="black", lty=5)
```

```{r}
# compare the distribution of averages of 40 exponentials to a normal distribution
qqnorm(means_exponentials)
qqline(means_exponentials, col = 2)
```


## Part 2


```{r}
data("ToothGrowth")
summary(ToothGrowth)
```

```{r}
table(ToothGrowth)
```


```{r}
vitaminC <- subset(ToothGrowth, supp == 'VC')
orangeJ <- subset(ToothGrowth, supp == 'OJ')
t.test(vitaminC$len, orangeJ$len, paired = FALSE, var.equal = FALSE)
dose05 <- ToothGrowth$len[ToothGrowth$dose == 0.5]
dose1 <- ToothGrowth$len[ToothGrowth$dose == 1.0]
dose2 <- ToothGrowth$len[ToothGrowth$dose == 2.0]
t.test(dose05, dose1 )
t.test(dose05, dose2)
t.test(dose1, dose2)
```
   
```{r}
dose05VC <- vitaminC$len[vitaminC$dose == 0.5]
dose1VC <- vitaminC$len[vitaminC$dose == 1.0]
dose2VC <- vitaminC$len[vitaminC$dose == 2.0]
dose05OJ <- orangeJ$len[orangeJ$dose == 0.5]
dose1OJ <- orangeJ$len[orangeJ$dose == 1.0]
dose2OJ <- orangeJ$len[orangeJ$dose == 2.0]
```
```{r}
t.test(dose05VC, dose05OJ)
t.test(dose1VC, dose1OJ)
t.test(dose2VC, dose2OJ)
```
   
#Conclusions:
Supplement type alone does not affect the mean value of length of odontoblasts. Dose level alone, without consideraton of supplement type affects tooth growth significantly. Increasing the dosage will induce better tooth growth. Orange Juice as a supplement, when used in dose levels of 0.5 mg/day and 1mg/day promotes better tooth growth than ascorbic acid. When applied in dose level of 2 mg/day, it has an effect on tooth growth similar to that of an ascorbic acid.